%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Wei-Sheng Wang (Wilson Wang)} \\ \vspace{1pt}
    \small \href{mailto:josixwang@gmail.com}{\underline{josixwang@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/josixwang/}{\underline{linkedin.com/in/josixwang}} $|$
    \href{https://josix.tw}{\underline{josix.tw}} $|$
    \href{https://github.com/josix}{\underline{github.com/josix}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant (Part-Time)}{Oct. 2017 -- Present}
      {National Chengchi University, CLIP Lab}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed a recommendation algorithm for KKTIX, the online ticketing platform under KKBOX Group}
        \resumeItem{Designed {\it Preference-Content Convolution (PCC)} graph learning algorithm and validated it through {\it Query-Based} experiments }
        \resumeItem{PCC increase precision by 2.5 times in offline testing and it is deployed and launched in August 2019}
        \resumeItem{Developed a full-stack recommender system using Django, ReactJS, and ElasticSearch}
      \resumeItemListEnd
    \resumeSubheading
      {Server Administration}{Aug. 2019 -- Present}
      {National Chengchi University, CLIP Lab}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Manage server accounts through building NIS server}
        \resumeItem{Avoid brute-force attack through configuring Fail2ban and sshd\_config configurations}
        \resumeItem{Built a sandbox environment for external data delivery through ChrootDirectory}
      \resumeItemListEnd
    \resumeSubheading
      {Cloud Support Engineer Intern}{Feb. 2020 -- Feb. 2021}
      {Amazon Web Services (AWS)}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Improved support engineer working process through building automated scripts}
        \resumeItem{Implemented multilingual sentences clustering to improve language translation quality}
        \resumeItem{Cooperate with overseas teams in Seattle}
        \resumeItem{Technical stacks - JavaScript, GreaseMonkey, DynamoDB, S3}
      \resumeItemListEnd
    \resumeSubheading
      {Frontend Developer (Contractor)}{Feb. 2020 -- May. 2020}
      {PAMO Law Office}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Modularize the legacy code to be more maintainable}
        \resumeItem{Refactor class to function components and Hooks in ReactJS}
        \resumeItem{Technical stacks - ReactJS, Redux, Create React App, RxJS}
      \resumeItemListEnd
    \resumeSubheading
      {Frontend Developer Intern}{Aug. 2017 -- Jun. 2018}
      {Rytass Corp.}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed CMS user interface including form validation, image uploader, article lists, etc.}
        \resumeItem{Developed RWD layout for the client websites}
        \resumeItem{Collaborate with backend developers to design and implement RESTful API and Graph API}
        \resumeItem{Technical stacks - ReactJS, Redux, react-apollo, Webpack, Babel}
      \resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd




%-----------PROJECTS-----------

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading{\large{\textbf{Work Project}}}{}
      \resumeProjectHeading
         {\textbf{MOST Review Candidate Recommendation} $|$ \emph{Django, React, Docker, Elasticsearch}}{Jun. 2019 -- Jan. 2020}
      \resumeItemListStart
        \resumeItem{Developed backend API and user interface for recommendation service}
        \resumeItem{Designed re-ranking recommendation mechanism that combining keyword-based recommendations and ML-based recommendations}
      \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{KKTIX Cold Start Recommendation}  \emph{\href{https://github.com/josix/NEPT}{- project link}} $|$ \emph{Python, Graph Embedding}}  {Oct. 2017 -- Feb. 2019}
        \resumeItemListStart
        \resumeItem{Developed {\it Preference-Content Convolution (PCC)} graph learning algorithm and the offline testing experiments}
        \resumeItem{Developed a full workflow for running data preprocessing, training, testing}
        \resumeItemListEnd
      \resumeProjectHeading{\large{\textbf{Open Source Contributions}}}{}
      \resumeProjectHeading
        {\textbf{commitizen-tools}  \emph{\href{https://commitizen-tools.github.io/commitizen/}{- project link}} $|$  \emph{Python, Poetry, pre-commit}}  {June 2020 - Present}
        \resumeItemListStart
           \resumeItem{A tool to define a standard way of committing rules and communicating them through CLI}
           \resumeItem{Reinforce the check feature to check whether it conforms to the conventional writing and list the non-conforming ones}
           \resumeItem{Update to add more unit tests}
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{PyCon TW 2019 Official Website}  \emph{\href{https://tw.pycon.org/2019/zh-hant/}{- project link}} $|$  \emph{Django, Saas}}  {Feb. 2019 - Sep. 2019}
        \resumeItemListStart
           \resumeItem{Responsible for developing the landing page, navigation bar, ticketing page}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Warehouse Translation}  \emph{\href{https://hosted.weblate.org/projects/pypa/warehouse/zh_Hant/}{- project link}}}  {Sep. 2019 - Feb. 2020}
        \resumeItemListStart
           \resumeItem{Add zh-tw translations to the new versioned PyPI (warehouse)}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Python Official Documents Translation}  \emph{\href{https://github.com/python/python-docs-zh-tw}{- project link}}}  {June 2018 - Oct. 2018}
        \resumeItemListStart
           \resumeItem{Responsible for translating chapter 9. Classes of the  tutorial to zh-tw}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Others} \emph{}}  {}
        \resumeItemListStart
           \resumeItem{\href{https://github.com/exercism/python}{exercism/python} - Update problem testcases} 
           \resumeItem{\href{https://github.com/pycontw/CCIP-HDP}{pycontw/CCIP-HDP}, \href{https://github.com/pycontw/session-video-publisher}{session-video-publisher} - Fix bugs} 
        \resumeItemListEnd

      \resumeProjectHeading{\large{\textbf{Side Project}}}{}
      \resumeProjectHeading
          {\textbf{Josix's Blog}  \emph{\href{https://josix.tw}{- project link}} $|$  \emph{Gatsby, Netlify}}  {Aug. 2020 - Present}
          \resumeItemListStart
            \resumeItem{Personal tech noting blog built by gatsby and netlify}
            \resumeItem{Features include GA tracking, simple SEO configuration, table of contents.}
            \resumeItem{Deep dive into tech tools like pyenv, pipx, etc.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Online Judge CLI}  \emph{\href{https://github.com/josix/oj-cli}{- project link}} $|$  \emph{Python, cURL}}  {Sep. 2020}
          \resumeItemListStart
            \resumeItem{Python based CLI that allowing students to upload their homework to the online judge system}
            \resumeItem{Features include authentication, uploading, downloading problems from the system}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
    
    
    
%-----------Community Involvement-----------

\section{Community Involvemnet}
    \resumeSubHeadingListStart
        \resumeProjectHeading{\large{\textbf{PyCon Taiwan}}}{Aug. 2019 -- Present}
        \resumeSubSubheading
         {Infra Squad Lead}{}
          \resumeItemListStart
            \resumeItem{Responsible for organizing team members to deliver tools for improving crew operation process}
          \resumeItemListEnd
        \resumeSubSubheading
         {Development Member}{}
          \resumeItemListStart
            \resumeItem{Developed official website through using Django and Sass}
            \resumeItem{Responsible for developing navigation bar, landing, ticketing page including RWD layout (2019)}
          \resumeItemListEnd
        \resumeProjectHeading{\large{\textbf{D4SG - Convenient Kanban for Wastewater Prevention}}}{Jul. 2017 -- Jan. 2018}
        \resumeSubSubheading
         {Volunteer}{}
          \resumeItemListStart
            \resumeItem{The plan aims to reduce the information gap between the Hsinchu County government, the public, and manufacturers, improve the efficiency of inspections, and promote the self-discipline of various manufacturers through public information.}
            \resumeItem{Responsible for crawling the company's financial report and display it in the kanban by using Selenium}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Chengchi University}{Taipei, Taiwan}
      {M.S. in Computer Science}{Feb.2020 -- Present}
    \resumeItemListStart
        \resumeItem{Members in Computational Linguistics and Information Processing Lab (CLIP Lab)}
        \resumeItem{Research interests span the areas of information retrieval, recommender systems, natural language processing}
        \resumeItem{\textbf{Related taken courses}:
        Distributed System, Cloud Big Data Service Practices, Web Search and Mining}
    \resumeItemListEnd
    \resumeSubheading
      {National Chengchi University}{Taipei, Taiwan}
      {B.S. in Computer Science and B.A. in Land Economics (Geometry Program)}{Sep. 2014 -- Feb. 2020}
    \resumeItemListStart
        \resumeItem{\textbf{Related taken courses}:
        Programming Language, Software Engineering, Database System}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python,  JavaScript, HTML/CSS, Shell Script, C/C++} \\
     \textbf{Libraries and Frameworks}{: Django, PyTorch, ReactJS, NumPy} \\
     \textbf{Developer Tools}{: zsh, Git, Docker, AWS, VS Code, ElasticSearch}
    }}
 \end{itemize}



%-------------------------------------------
\end{document}
