\subsection{{Open Source Contributions}}
\subtext{@apache/airflow}
\begin{zitemize}
\item Implemented the integration of OpenAI Batch API support in Apache Airflow, including creating a new hook, operator (deferrable compatible), and trigger, along with comprehensive unit testing and documentation updates. (\href{https://github.com/apache/airflow/pull/41554}{\#41554})
\item Implemented a tags filter feature for DAGs list in Apache Airflow, enhancing the UI as per \href{https://cwiki.apache.org/confluence/display/AIRFLOW/AIP-38+Modern+Web+Application}{AIP-38 Modern Web Application}. (\href{https://github.com/apache/airflow/pull/43303}{\#43303})
\item Resolved issues in Airflow Connection by preventing an AttributeError when setting up MongoDB connection and fixing an InvalidURL error in Airbyte hooks, enhancing the reliability and stability of the platform (\href{https://github.com/apache/airflow/pull/43024}{\#43024}, \href{https://github.com/apache/airflow/pull/38860}{\#38860})
\end{zitemize}
\subtext{@airbytehq}
\begin{zitemize}
\item Implemented the new source connector that ingests 5 different resources from ClickUp API through the low-code CDK with the passed acceptance test and complete documentation. (\href{https://github.com/airbytehq/airbyte/pull/17770}{\#17770})
\item Reported one extensibility issue that occurred when running acceptance test in python 3.10+ (\href{https://github.com/airbytehq/airbyte/issues/17855}{\#17855})
\end{zitemize}
\subtext{@python}
\begin{zitemize}
\item Co-organized the python documentation localization meetup regularly and increased the amount of translated documents by around +40\%
\end{zitemize}

\subsection{{PyCon Taiwan \hfill 2019 --- Present}}
\subtext{Web Squad Lead \hfill 2022 --- 2024}
\begin{zitemize}
  \item Coordinated around 8+ team members to play different roles like UI/UX designers, developers, and reviewers. Make sure the internal communication is smooth by building meeting minutes, onboarding docs, and feature docs to ensure the conversation is public and easy to access.
  \item Monitor work in the kanban board, make sure to deliver the features requested by the Program Team, Sponsor Team, Registering Team, etc. Distribute the tasks to the team members, and follow up on the progress.
\end{zitemize}

\subtext{Infra Squad Lead \hfill 2021 --- 2023}
\begin{zitemize}
\item Coordinated around 7 members to fit into the infra squad and help them understand and contribute to the projects by mentoring and 1-1 meetings.
\item Maintaining 4 projects \footnote{\href{https://github.com/pycontw/session-video-publisher}{session-video-publisher}, \href{https://github.com/pycontw/hackmd-archive-worker}{hackmd-archive-worker}, \href{https://github.com/pycontw/talk-preview-img-builder}{talk-preview-imag-builder}, and \href{https://github.com/pycontw/pycon_archive_past_website}{pycon-archive-past-website}} for supporting the Program Team, Web Team, and Committee to build an automatic workflow through CLI tools.
\end{zitemize}

\subtext{Developer \hfill 2019 --- Present}
\begin{zitemize}
\item Contributed to the \href{https://github.com/pycontw/pycon.tw}{pycon.tw} and \href{https://github.com/pycontw/pycontw-frontend}{pycontw-frontend}, including implementing the homepage, about, and sponsor page with the card, modal components, and the flexbox, grid layout.
\item Responsible for reviewing the opened PRs. Make sure that code uses the unified naming convention, and shared components, and check the functionalities and appearance work correctly. Giving the feedback following the \href{https://conventionalcomments.org/}{conventional comments} guideline.
\end{zitemize}